supplmental

### 2019-12-31 paper_stats.Rmd
update analysis

---
title: ''
author: ''
date: ''
output:
  word_document:
    reference_docx: style.1.docx
  html_document:
    df_print: paged
---

@@

  load("scripts/models_dec_2019.RData")

@@

# Just print the estimates and 95%CI from the models  
  des_est <- function(model){
    x <- broom::tidy(model) %>% 
      mutate(estimate = signif(estimate, 2), 
             ul = signif(estimate + (1.96 * std.error), 3), 
             ll = signif(estimate - (1.96 * std.error), 3)) %>%
      filter(term == "tx2")

@@

  within_diffs <- function(data, var){
    select(data, subj_id, tx, ep) %>% 
    mutate(tx = factor(tx, labels = c("Control", "Active"))) %>%
    spread(tx, ep) %>% 
    mutate(effect = Active - Control) %>% 
    filter(!is.na(effect)) %>%
    summarise(Mean_diff = signif(mean(effect, na.rm = TRUE), 2),
              SD_diff = signif(sd(effect, na.rm = TRUE), 2), 
              n_diff = n(), 
              Outcome = var) %>% 
    select(Outcome, n_diff, Mean_diff, SD_diff) %>%
    return()
  }

@@

  get_p <- function(model){
    x <- sjstats::p_value(model) %>% filter(term == "tx2")
    return(signif(x$p.value, 2))
    }

@@

  des_est2 <- function(model, varname){
    x <- broom::tidy(model) %>% 
      mutate(estimate = signif(estimate, 2), 
             ul = signif(estimate + (1.96 * std.error), 3), 
             ll = signif(estimate - (1.96 * std.error), 3), 
             var = varname) %>%
      filter(term == "tx2")

@@

    ggsave("plots/primary/all.pdf", width = 33.867, height = 19.05, units = "cm",
         scale = 0.6, dpi = 600)

@@

  ggsave("plots/primary/sbp.pdf", width = 33.867, height = 19.05, units = "cm",
         scale = 0.6, dpi = 600)
```

@@

  var_ratio <- function(df, var_lab, logged, ...){

@@

  var_ratio(sbp, "SBP")

@@

  dist(sbp, "SBP (mmHg)") +
    ggtitle("Systolic Blood Pressure")

  dist(dbp, "DBP (mmHg)", logged = "no") +
    ggtitle("Diastolic Blood Pressure")

  dist(oxldl, "Log(OXLDL)", logged = "yes") +
    ggtitle("OXDL")

  dist(art_stif, "Arterial Stiffness", logged = "no")+
    ggtitle("Arterial Stiffness")

  dist(glu, "Glucose", logged = "no") +
    ggtitle("Glucose")

  dist(ldl, "LDL", logged = "no") +
    ggtitle("LDL")

  dist(hdl, "Log(HDL)", logged = "yes") +
    ggtitle("HDL")

  dist(tchol, "Log(TCHOL)", logged = "yes")+
    ggtitle("Total cholesterol")

  dist(tag, "Log(TAG)", logged = "yes")+
    ggtitle("TAG")

  dist(pwa_augment, "PWA Augment", logged = "no")+
    ggtitle("Diastolic Blood Pressure")

>>>>

---
title: ''
author: ''
date: ''
output:
  word_document:
    reference_docx: style.1.docx
  html_document:
    df_print: paged
    keep_md: true
---

@@

# load("scripts/models_dec_2019.RData")
  source("scripts/01_project.R") # Produces the model and data objects

@@

# Just print the estimates and 95%CI from the models  
  des_est <- function(model){
    x <- broom::tidy(model) %>% 
      mutate(estimate = signif(estimate, 2), 
             ul = signif(estimate + (1.96 * std.error), 3), 
             ll = signif(estimate - (1.96 * std.error), 3)) %>%
      filter(term == "txActive")

@@

  within_diffs <- function(data, var){
    select(data, subj_id, tx, ep) %>% 
    spread(tx, ep) %>% 
    mutate(effect = Active - Control) %>% 
    filter(!is.na(effect)) %>%
    summarise(Mean_diff = signif(mean(effect, na.rm = TRUE), 2),
              SD_diff = signif(sd(effect, na.rm = TRUE), 2), 
              n_diff = n(), 
              Outcome = var) %>% 
    select(Outcome, n_diff, Mean_diff, SD_diff) %>%
    return()
  }

@@

  get_p <- function(model){
    x <- sjstats::p_value(model) %>% filter(term == "txActive")
    return(signif(x$p.value, 2))
    }

@@

  des_est2 <- function(model, varname){
    x <- broom::tidy(model) %>% 
      mutate(estimate = signif(estimate, 2), 
             ul = signif(estimate + (1.96 * std.error), 3), 
             ll = signif(estimate - (1.96 * std.error), 3), 
             var = varname) %>%
      filter(term == "txActive")

@@

# ggsave("plots/primary/all.pdf", width = 33.867, height = 19.05, units = "cm",
#      scale = 0.6, dpi = 600)

@@

# ggsave("plots/primary/sbp.pdf", width = 33.867, height = 19.05, units = "cm",
#        scale = 0.6, dpi = 600)
```

@@

  var_ratio <- function(df, var_lab, logged = "No", ...){

@@

# var_ratio(sbp, "SBP")

@@

  # dist(sbp, "SBP (mmHg)") +
  #   ggtitle("Systolic Blood Pressure")
  # 
  # dist(dbp, "DBP (mmHg)", logged = "no") +
  #   ggtitle("Diastolic Blood Pressure")
  # 
  # dist(oxldl, "Log(OXLDL)", logged = "yes") +
  #   ggtitle("OXDL")
  # 
  # dist(art_stif, "Arterial Stiffness", logged = "no")+
  #   ggtitle("Arterial Stiffness")
  # 
  # dist(glu, "Glucose", logged = "no") +
  #   ggtitle("Glucose")
  # 
  # dist(ldl, "LDL", logged = "no") +
  #   ggtitle("LDL")
  # 
  # dist(hdl, "Log(HDL)", logged = "yes") +
  #   ggtitle("HDL")
  # 
  # dist(tchol, "Log(TCHOL)", logged = "yes")+
  #   ggtitle("Total cholesterol")
  # 
  # dist(tag, "Log(TAG)", logged = "yes")+
  #   ggtitle("TAG")
  # 
  # dist(pwa_augment, "PWA Augment", logged = "no")+
  #   ggtitle("Diastolic Blood Pressure")
  #
